---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"

authornote: |
  Enter author note here.

abstract: |
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}
    
    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother
  - \usepackage{pdflscape}

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
classoption       : "stu, a4paper"
output            : papaja::apa6_pdf

---

```{r setup, include = FALSE}
library("papaja")
library(RefManageR)
library(kableExtra)
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```


```{r include = TRUE, results = "asis"}
# Create the data frame with the necessary columns
new_table <- data.frame(
  Citation = character(),
  Study_Design = character(),
  Population = character(),
  Questions = character(),
  Variables = character(),
  data_analysis = character(),
  results = character(),
  review = character(),
  stringsAsFactors = FALSE
)

# Example entry for manual filling (you will need to fill these with the actual data)
new_table[1, ] <- c(
  "Beilock et al. (2007)",
  "Experimental",
  "100 college students, mixed gender",
  "Behavioral tasks, fMRI",
  "Stereotype threat impairs working memory efficiency",
  "Prefrontal cortex, phonological loop",
  "Reduced performance on cognitive tasks under threat",
  "yes"
)

# Create the apa_table object
apa_table(
  new_table,
  caption = "Overview of the Included Papers for Hypothesis 1",
  longtable = TRUE,
  escape = FALSE,
  landscape = TRUE,
  col.names = c(
    "Citation",
    "Study Design",
    "Population",
    "Research Questions",
    "Variables",
    "Methods of Data Analysis",
    "Results",
    "Hypothesis confirmed"
  ),
  align = c("m{1.5cm}", "m{3cm}", "m{2.5cm}", "m{3cm}", "m{3cm}", "m{3cm}", "m{3.5cm}", "m{1.5cm}"),
  note = "Note: Some column headers span multiple lines for better readability."
)
```


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

```{r include = TRUE, results = "asis"}

query_table <- data.frame(
     Hypothesis = character(),
     Query = character()
)

colnames(query_table) <- c(
     "Hypothesis",
     "Query"
)

query_table[1, ] <- c(
     "Hypothesis 1",
     "SELECT * FROM papers WHERE hypothesis = 1"
)

apa_table(query_table,
          escape = TRUE,
          small = T
          )

```

# HELLO WORLD

```{r include = FALSE}
source("analysis-test.R")
```

This is the anova result: `r yep$statistic`.


## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


Here, a sample of thirty-three ($N = 33$) women performed, both, vertical and horizontal MA tasks.
Similar to Experiment 1 they were introduced to the subject with a practice block, followed by a baseline block and a posttest block. 
This time, all participants received the stereotype threat manipulation in between the last two blocks but were randomly assigned to either the vertical or horizontal problem condition.
Afterwards, they were given questionnaires to assess their thought during the stereotype threat manipulation, their perceived importance of task performance, and their state anxiety following stereotype threat. 
The independent variables consisted of Block (baseline vs. stereotype threat), Problem working memory demand (low vs. high), and Problem orientation (horiztonal vs. vertical), while the dependent variables were maths problem accuracy, reaction times, and self-reported thoughts/worries.
Neither the perceived importance of performing well (vertical: *M* = 4.67, *SE* = `r apa_num(0.35)`; horizontal: *M* = 5.27, *SE* = `r apa_num(0.37)`) nor state anxiety differed between the groups (vertical: *M* = `r apa_num(33.22)`, *SE* = 1.6; horizontal: *M* = `r apa_num(37.00)`, *SE* = 2.7), *F*(1,31) = 1.53, *p* = `r apa_p(.22)`.
Thoughts/worries were split into four categories, most common were thoughts about the performance monitoring (34.9%), followed by thoughts related about the processes involved in solving the problems (32.4%), unrelated thoughts made up 18.3% and, lastly, 14.5% of the thoughts related to the stereotype threat manipulation.
Again, no significant difference between the groups was found (Categories 1, 3, and 4: *F* < 1; Category 2: *F*(1,31) = 2.17, *p* = `r apa_p(.15)`.)  
For the MA problems, a three-way interaction between the independent variables was found, *F*(1,31) = 4.12, *p* = `r apa_p(.05)`, $\eta^{2}_{p}$ = `r apa_num(.12)`.  
Similar to Experiment 1, a significant $\text{Block } \times \text{Problem Demand }$ interaction was found but only for horizontal problems, *F*(1,14) = 7.70, *p* < `r apa_p(.02)`, $\eta^{2}_{p}$ = `r apa_num(.36)`.
Accuracy suffered significantly from the baseline (*M* = 91.7%, *SE* = 3.6%) to the stereotype threat (*M* = 81.2%, SE = 4.6%) block; CI [`r apa_num(84)`% - `r apa_num(99.3)`%]; *d* = `r apa_num(.64)`. 
The three-way ANOVA for, RTs revealed that high-demand problems were slower, compared to low-demand problems; vertical: *F*(1,17) = 306.32, *p* < `r apa_p(.01)`, $\eta^{2}_{p}$ = `r apa_num(.95)`; horizontal: *F*(1,14) = 11.04, *p* < `r apa_p(.01)`, $\eta^{2}_{p}$ = `r apa_num(.44)`.
This effect was not significant for horizontal problems and revealed a main effect for vertical problems.  
It is concluded that low-demand problems do not suffer under stereotype threat, however, the working memory is impaired for high-demand problems resulting in a decrease in accuracy (only for horizontal problems) and an increase in reaction time.  

#### Experiment 4
All thirty ($N = 30$) women were tasked to solve horizontal and vertical MA under stereotype threat.
Procedure was similar to Experiment 3A, albeit, with a bigger practice block, and the repetition of some problems.
The independent variables consisted of Block (baseline vs. stereotype threat), Problem Repetition (no repeat vs. multiple repeat), and Problem Working Memory demand (low vs. high), while the dependent variables did not differ from Experiment 1.  
The significant $\text{Block } \times \text{ Problem Repetition } \times \text{ Problem Working Memory demand }$ interaction, *F*(1, 29) = 6.13, *p* < `r apa_p(.02)`, $\eta^{2}_{p}$ = `r apa_num(.17)`, was further analysed by differentiating between multi- and no=repeat problems.  
For the multi-repeat problems no significant interaction was to be found (*F* < 1), meanwhile a significant effect was found for the no-repeat problems, *F*(1,29) = 11.11, *p* < `r apa_num(.01)`, $\eta^{2}_{p}$ = `r apa_num(.28)`.
While the accuracy, again, significantly decreased from the baseline (*M* = `r apa_num(65)`%, *SE* = 3.9%) to the stereotype threat block (*M* = `r apa_num(65)`%, *SE* = 5.9%; CI [`r apa_num(52.8)`% - `r apa_num(77.2)`%]; *d* = `r apa_num(.70)`) in high-demand problems, within the no-repeat condition, no significant effect was found for the low-demand problems (baseline: *M* = `r apa_num(95.0)`%, *SE* = `r apa_num(1.5)`%, stereotype threat: *M* = `r apa_num(94.8)`%, *SE* = `r apa_num(2.8)`%).
For the RTs, problem demand, *F*(1,26) = 144.14, *p* < `r apa_p(.01)`, $\eta^{2}_{p}$ = `r apa_num(.85)`, influenced the RTs more than problem repetition,*F*(1,26) = 139.94, *p* < `r apa_p(.01)`, $\eta^{2}_{p}$ = `r apa_num(.84)`, both showing main effects.  
Based on these results, the authors conclude that practised, horizontal problems do not rely on working memory heavily, evidenced by them not being affected by stereotype threat.
The opposite is true for no-repeat problems, which did suffer under stereotype threat, given that they were of high verbal working memory demand.  

#### Experiment 5  
The last experiment was preceded by a pilot test to establish whether the two-back tasks were of equal difficulty.
This pilot test was done with $N = 27$ women, without any stereotype threat manipulation, the procedure is similar to the main experiment, thus will not be discussed further.  
The main experiment consisted of thirty-three ($N = 33$) women.
Upon arrival participants completed a two-back practise task, after changing computers, they practised the MA task.
Afterwards, the stereotype threat manipulation was performed, followed by twenty high-demand horizontal problems.
In the next step, participants went back to the first computer to complete 100 trails of the same version of the two-back task that was practised before.  
Condition (stereotype threat vs. control; control being the pilot test) and Two-back task type (verbal vs. spatial) functioned as independent variables, while the dependent variables were accuracy and reaction time, each for, both, the maths problem and the two-back task.  
Comparing the MA results with the previous experiments results for the same type of task (horizontal, high-demand), showed that the stereotype threat significantly inhibited performance (*M* = `r apa_num(82.2`%, *SE* = `r apa_num(2.0)`%), while the same cannot be said for the no-threat conditions (*M* = `r apa_num(91.5)`%, *SE* = `r apa_num(1.5)`%).  
For the two-back task, RTs between spatial (*M* = 895 ms, *SE* = 49 ms) and verbal (*M* = 1087 ms, *SE* = 59 ms) task differed significantly, *F*(1,31) = 6.133, *p* < `r apa_p(.02)`, $\eta^{2}_{p}$ = `r apa_num(.17)` while the difference in accuracy did not reach significance (verbal: *M* = `r apa_num(87.3)`%, *SE* = `r apa_num(1.7)`%; spatial: *M* = `r apa_num(89.0)`%, *SE* = `r apa_num(1.5)`%, *F* < 1).
Comparing the performance of the stereotype threat condition with the control (pilot test), showed an interaction between $\text{Task } \times \text{ Experiment }$ for RT, *F*(1,56) = 4.38, *p* < `r apa_p(.05)`, $\eta^{2}_{p}$ = `r apa_num(.07)`.
Without stereotype threat, no significant differences in performance between thee verbal and spatial two-back tasks were found, however, under stereotype threat the verbal task was significantly slower than the spatial task.  
Contrary to the previous Experiments, Experiment 5 additionally aimed to investigate whether stereotype threat has a spill over effect on unrelated tasks.
Since these results are not relevant to the hypotheses of this review, they will not be discussed in detail.
Using multiple regression analyses the authors found that the stereotype threat did indeed spill over to the two-back task, however, only for the verbal task.  
According to the authors, the results of the different Experiments in this paper, show stereotype threats effect on working memory, they mention that "especially the phonological aspects" are affected.
Stereotype threat's effect onto task-related worries as well as thoughts serve as further indications for this conclusion.
Further, it is concluded that stereotype threat likely affects multiple aspects of working memory. 
A combination of phonological loop and central executive functioning is suggested to be affected by stereotype threat.  
H1 is partially confirmed by this paper, central executive functioning is assumed to involve the prefrontal cortex, however, this is not the only area affected. 
The phonological loop is associated with BA4, BA49, and (approximately) BA44 and BA 45.


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
