---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

note: "\\clearpage"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  < !-- https://tinyurl.com/ybremelq -- >
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "files/references.bib"]
annotate_references: yes
nocite            : |
  @R-base

floatsintext      : yes 
linenumbers       : no
draft             : no
mask              : no

figurelist        : yes
tablelist         : yes
footnotelist      : no

header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}
    
    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother
    \setlength{\cslhangindent}{0.5in}
    \usepackage{fancyhdr} 
    \pagestyle{fancy}   
    \fancyhf{} 
    \fancyhead[R]{\thepage} 
    \renewcommand{\headrulewidth}{0pt}
    \thispagestyle{fancy}
    \duedate{07.08.2023}
    \course{Modul 6b: Empirisch-Experimentelles Praktikum}
    \professor{Dr. }
  - \usepackage{pdflscape}



csl               : "`r system.file('rmd', 'apa7-annotated.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
classoption       : "stu, a4paper"
language          : "en-GB"
---


```{r setup, include = FALSE}
library("papaja")
library("citr")
library("rmarkdown")
r_refs("r-references.bib")
```

# Methods

## Preregistration and version control

The hypotheses, the inclusion/exclusion criteria, used databases, search queries and the basic theoretical foundation of this systematic literature review are preregistered and can be found on Moodle or in the GitHub repository.  
As suggested by @lakensImprovingYourStatistical2022 (Chapter 14), the present systemic literature used a GitHub repository to store all data and files. The repository is available at: https://github.com/julianrottenberg/Stereotype_Threat_im_akademischen_Kontext  
This approach allows for more transparency and reproducibility, as well as accountability.  

## Artificial Intelligence (AI)

It should be acknowledged that artificial intelligence has been used as an aid in this review — namely, Anthropic's Claude AI 3.5 Sonnet [@anthropicClaudeAiSonnet2024] and GitHub's Copilot [@githubGitHubCopilot2024], the latter was directly integrated into RStudio Server [@positteamRStudioIntegratedDevelopment2024]. The chats that directly influenced this review are all available on the GitHub repository.
For GitHub Copilot, the autocomplete-style suggestions were used.  
Claude AI 3.5 Sonnet was used to generate descriptions of the papers used in this review — based on a template, further, follow-up questions were asked to clear up uncertainties.
The process here was as follows: First the template was manually filled out by a human, after this process was completed for every paper, a second template was created, the contents of which were filled out by AI and then, later, used with the manually created templates. When the different templates differed from one another, the primary source (i.e. the paper the template was based on) was checked again. Both, the human-generated and the AI-generated templates can be found on the GitHub repository — the AI-generated summaries have been marked as such, beginning with "Claude_Ai_" in their file name.  
To clarify, AI was not used to generate any of the text in this review, it was used as a tool to gather a better understanding and overview of the papers involved. The process of having a human and AI create a summary of each paper was chosen to gather an extra layer of security regarding the contents of each paper, as well as to counteract possible oversights.  


## Databases, search queries and inclusion/exclusion criteria

The databases used were Web of Science, Google Scholar, PSYNDEX, ResearchRabbit and EBSCOhost Within EBSCOhost, the databases  APA PsycArticles, APA PsycInfo, Psychology and Behavioral Sciences Collection, PSYNDEX Literature with PSYNDEX Tests, Education Source Ultimate, and Academic Search Ultimate were searched.  
Furthermore, the snowball method was utilized to find additional papers — however, this approach did not deliver any additional papers, the same applies to ResearchRabbit.  
The permalinks to each search used can also be found within the GitHub repository.  
Within Web of Science the included document types were "Article", "Other", or "Clinical Trail"; the excluded document types were "Book", "Meeting", "Editorial Material", or "Review Article".
Furthermore, the database "Preprint Citation Index" was excluded.  
In EBSCOhost, "Apply equivalent subjects" was applied as an Expander, while "Peer Reviewed", "Document Type\*", and "Publication Type\*" were used as Limiters.  
In Google Scholar, the following was added at the end of the search query: 'AND "empirical study" AND "peer-reviewed" -books -meta-analysis)'.  
These extra filters were applied in accordance with the inclusion and exclusion criteria outlined in the preregistration. No other changes were made to the search queries. An overview of the search queries can be found in Table \ref{tab:query_table}.

```{r query_table, include = TRUE}

query_table <- data.frame(
  Hypothesis = character(),
  Query = character(),
  stringsAsFactors = FALSE
)

colnames(query_table) <- c("Hypothesis", "Search Query")

query_table[1, ] <- c(
  "H1",
  '("stereotype threat") AND 
(neural OR neuroimaging OR "functional magnetic resonance imaging" OR fMRI OR electroencephalo* OR EEG OR ERP OR "brain activation" OR amygdala OR "prefrontal cortex" OR "default mode network" OR "salience network") AND
(academ* OR education* OR stud* OR learn* OR perform* OR school OR university OR college)'
)

query_table[2, ] <- c(
  "H2",
  '("stereotype threat") AND 
("cognitive control" OR "executive function" OR "executive function network" OR "cognitive control network" OR "brain activation" OR "brain activation patterns" OR "cognitive tasks" OR "executive tasks" OR "cognitive assessment" OR "executive assessment") AND 
(academ* OR education* OR stud* OR learn* OR perform* OR school OR university OR college)'
)

query_table[3, ] <- c(
  "H3",
  '("stereotype threat") AND 
("working memory*" OR "processing speed" OR accuracy) AND 
(academ* OR education* OR stud* OR learn* OR perform* OR school OR university OR college)'
)

apa_table(query_table, 
          caption = "Search queries used for the systematic literature review.",
          note = "The search queries were used in the databases Web of Science, Google Scholar, PSYNDEX, ResearchRabbit, and EBSCOhost. The permalinks to each search used can be found within the GitHub repository.",
          escape = TRUE,
          align = c("m{4cm}", "m{12cm}"),
)

```

The inclusion and exclusion criteria specified in the preregistration were applied to each paper. 
The criteria "Stereotype Threat", which required studies to "explicitly examine, manipulate, or measure stereotype threat as a key study variable or factor" was enforced on plenty of papers and resulted in their exclusion — even when they were otherwise relevant (more on this in the discussion section), same applies to the "Outcomes" criteria, which required studies to report "at least one of the following: 1. Neural activation patterns/brain imaging data; 2. Cognitive processes (e.g., working memory, cognitive control/executive functions)" also resulted in the exclusion of papers which indirectly measured these outcomes but/or did not specifically focus on "working memory" for example — as an example: a paper might have used a test that is known to measure working memory but did not mention "working memory" within its abstract, methods or results section, so it was excluded.  

## Screening and paper details

The screening process was done using the software Rayyan [@ouzzaniRayyanWebMobile2016]. All results were imported onto the platform. 
The total number of papers found was 600 ($N = 600$, $n_{\text{EBSCOhost}} = 105$, $n_{\text{Google Scholar}} = 48$, $n_{\text{PSYNDEX}} = 5$, $n_{\text{ResearchRabbit}} = 5$, $n_{\text{Web of Science}} = 437$). Out of these, 83 were duplicates (88 were automatically detected by Rayyan; however, 5 were false positives), leaving 517 papers to be screened. During the first screening, another 440 papers were excluded. 
Papers which were excluded did not fit the inclusion criteria, most prominently, they either did not focus on stereotype threat, had the wrong population (e.g., older adults), did not fit the publication type requirements, or did not measure the outcomes of interest — this was assessed using the title, keywords, and abstract. If neither the title nor the keywords or abstract mentioned enough information to make a decision, the paper was marked as 'maybe. 
An example for Hypothesis 3 would be, a paper measured working memory but just referred to "the participants" in the abstract, without clarifying that they fit the definition of the academic context. After this first screening, 77 papers remained for the second screening.
This second screening was done by looking into the full-text of each paper, here another 49 papers were excluded for the following reasons: wrong focus ($n = 30$), wrong study design ($n = 10$), wrong population ($n = 7$), wrong publication type ($n = 2$) — an overview of this can be found in the PRISMA flowchart [@haddawayPRISMA2020PackageShiny2022] in Figure \ref{fig:prisma}.
In the end, 28 papers were included in this review, $n = 8$ for Hypothesis 1, $n = 9$ for Hypothesis 2, and $n = 14$ for Hypothesis 3 — some were used for multiple hypotheses. Out of the 517 papers, 382 were excluded for 'wrong focus', 73 for 'wrong population', 43 for 'wrong study design', 13 for wrong publication type, 4 for 'foreign language', and 1 for 'wrong study duration' (some papers were excluded for multiple reasons). A full list of all papers found and excluded can be found in the GitHub repository.  
A template was created to summarize each paper, with two versions completed: one by the author and one by Claude AI. 
The template was a mixture of the following checklists: CASP systematic review checklist [@criticalappraisalskillsprogrammeCASPSystematicReview2018], Review guidelines for extracting data and quality assessing primary studies in educational research [@eppi-centreReviewGuidelinesExtracting2003], Critical appraisal checklist for a systematic review [@universityofglasgowCriticalAppraisalChecklistn.d.nodate], and the Newcastle-Ottawa scale (NOS) for assessing the quality of nonrandomised studies in meta-analyses [@wellsNewcastleottawaScaleNOS2014], which are used to describe studies and assess their quality.
Redundant and irrelevant items were eliminated, and the remaining questions were consolidated into a single template.
This approach provided a comprehensive overview of the final papers.
Based on these summaries, the papers were analysed, and the results are presented in the following sections.  

```{r prisma, fig.cap = "PRISMA flowchart of the screening process."}

knitr::include_graphics("files/prisma.pdf")
```

## Reporting of *p*-values  

It should be noted that some *p*-values are reported for example, *p* < `r apa_p(0.01)`, this is not in accordance with APA guidelines [@36DecimalFractions2020]; however, this format was chosen, since the papers it was taken from used this format, and it was deemed important to keep the original format, especially since it is unknown what the actual *p*-value was.

## RStudio and R packages

The following R packages were used to create this review: `r cite_r("r-references.bib")`.  
 
# Results

## Hypothesis 1: Stereotype threat, brain areas/networks, performance.

@beilockStereotypeThreatWorking2007 hypothesized that high-pressure situations would impair maths performance, especially under high working memory load.
The dependent variables were maths accuracy, self-reported thoughts, and reaction time (RT), while the independent variables were group (stereotype threat vs. control), problem working demand (low vs. high), block (baseline vs. post-test), and *2*-back task (verbal, spatial).
31 women participated in Experiment 1, 33 in Experiment 3A, and 30 in Experiment 4.
Experiment 1: Under threat, the Group $\times$ Block $\times$ Problem Demand interaction was found to be significant for accuracy, *F*(1,29) = 11.18, *p* < `r apa_p(0.01)`, $\eta^{2}_{p}$ = `r apa_p(.28)`.
High-demand problems, showed a significant decrease in accuracy at the post-test, CI [`r apa_num(81)`% - `r apa_num(97)`%]; *d* = `r apa_num(.61)`.  
Experiment 3A: For the MA problems, a three-way interaction between the independent variables was found, *F*(1,31) = 4.12, *p* = `r apa_p(.05)`, $\eta^{2}_{p}$ = `r apa_p(.12)`.
Accuracy suffered significantly under stereotype threat; CI [`r apa_num(84)`% - `r apa_num(99.3)`%]; *d* = `r apa_num(.64)`.   
Experiment 4: A significant Block $\times$ Problem Repetition $\times$ Problem Working Memory demand interaction was found, *F*(1, 29) = 6.13, *p* < `r apa_p(.02)`.
Accuracy significantly decreased under stereotype threat; CI [`r apa_num(52.8)`% - `r apa_num(77.2)`%]; *d* = `r apa_num(.70)`) in high-demand problems.  
Experiment 5: Under stereotype threat, an interaction between Task $\times$ Experiment for RT, *F*(1,56) = `r apa_num(4.38)`, *p* < `r apa_p(.05)`, $\eta^{2}_{p}$ = `r apa_p(.07)` was found, with verbal tasks being significantly slower than spatial ones.
H1 is partially confirmed by this paper, central executive functioning is assumed to involve the prefrontal cortex; however, this is not the only area affected. 
The phonological loop is associated with BA4, BA49, and (approximately) BA44 and BA45.  

@dunstSexDifferencesNeural2013 investigated the effects of stereotype threat on neural efficiency and sex differences in visuospatial task performance, using task performance, brain activation, and neural efficiency as dependent variables, and sex, stereotype exposure, and figural intelligence as independent variables
The final sample consisted of 58 participants ($N = 58$; 26 girls).
The TRP changes revealed a main effect for Stereotype Exposure (*F*(1, 54) = 3.93, *p* = `r apa_p(.05)`, $\text{partial }\eta^{2}$ = `r apa_num(.07)`), with heightened cortical activation (*M* = `r apa_num(0.07)`, *SD* = `r apa_num(0.03)`) in the stereotype threat condition. 
H1 is not confirmed by this paper, as the only significant effect under stereotype threat was an increase in cortical activation, which are regions of the cerebral cortex or cerebellar cortex [@americanpsychologicalassociationCorticalActivation2018].  

In a sample of 58 participants (33 minorities), @forbesSpontaneousDefaultMode2015 investigated how DMN phase-locking at rest affects stereotype threat's impact on performance perceptions in minorities versus Whites.
Besides ethnicity (Minority vs. White), the independent variables consisted of the phase-locking between the left lateral parietal cortex (LLPC) and precuneus/posterior cingulate cortex (P/PCC), and the phase-locking between LLPC and the medial prefrontal cortex (MPFC), each at the frequency bands alpha (8-12 Hz) and theta (4-8 Hz), these will also be referred to as DMN phase-locking, if the need to differentiate between them is not given.
Error estimates and self-doubt were used as dependent variables.  
The relationship between LLPC-P/PCC theta phase-locking showed a main effect on error estimation (*b* = -`r apa_num(195.29)`, $\beta$ = -`r apa_num(0.37)`, *SE* = `r apa_num(81.13)`, *p* = `r apa_p(0.021)`), which was then moderated by a significant interaction (*b* = `r apa_num(350.13)`, $\beta$ = `r apa_num(0.37)`, *SE* = `r apa_num(147.26)`, *p* = `r apa_p(0.021)`).
Among minorities, a correlation between LLPC-MPFC theta phase-locking and self-doubt was found to be significant (*r* = -`r apa_num(0.54)`, *p* < `r apa_p(0.01)`), differing significantly from Whites (*z* = -`r apa_num(2.0)`, *p* < `r apa_p(0.05)`.
H1 is supported by this paper.

@forbesRoleDevaluingDiscounting2008 hypothesized that error-related negativity (ERN) displays a greater amplitude under stereotype threat, and that greater Error Positivity (Pe) amplitudes to errors would be predicted under stereotype threat.  
The study design was cross-sectional with two groups, diagnostic of intelligence (DIQ; stereotype threat) and control (no stereotype threat).
Diagnostic of intelligence (DIQ; stereotype threat) and control, alongside psychological disengagement (devaluing academics/discounting intelligence tests) were the independent variables and ERN, Pe, task performance, and self-reported measurements were the dependent variables.
The sample consisted of 57 ($N = 57$) minority undergraduates.
The ERN was measured as the peak negative deflection at Fz (frontal midline electrode) between 50 and 130 ms after the response, while the Pe was measured as the peak positive deflection at site Pz (midline parietal electrode) between 200 and 500 ms after the error, based on these difference waveforms.
Under stereotype threat ($\beta$ = `r apa_num(0.46)`, *p* < `r apa_p(0.01)`), smaller ERN amplitudes were found, with devaluing was a predictor.
On Pe amplitudes a significant moderation effect of discounting on diagnosticity was observed at Pz, $\beta$ = `r apa_num(0.29)`, *p* < `r apa_p(0.03)`, $R^2$ = `r apa_num(0.52)`).
If participants were low in discounting ($\beta_{Low}$ = -`r apa_p(0.39)`, *p* < `r apa_num(0.04)`), smaller Pe amplitudes were found under stereotype threat.
In the opposite case, i.e. high discounting ($\beta_{High}$ = `r apa_num(0.20)`, *p* = `r apa_p(0.23)`), participants showed larger Pe amplitudes.
H1 is partially being confirmed by this paper, as neural activation was found due to stereotype threat; however, the results for the affected areas are more vague, being linked to the anterior cingulate of the prefrontal cortex.

@jonczykHowStereotypeThreat2022 examined the impact of stereotype threat on alpha power and creative thinking in 23 female undergraduates. 
Measurements were taken before and after threat manipulation, forming the independent variables, while creative thinking (measured using Alternative Uses task; AUT, and Utopian Situations task; UST) and alpha power formed the dependent variables.
Task related power (TRP) was calculated in the lower (8-10 Hz) and upper (10-12 Hz) alpha bands before and after the stereotype threat manipulation.  
The final sample consisted of twenty-three ($N = 23$) female undergraduates.  
A main effect of threat was found in the lower alpha range (8-10 Hz), *F*(1,21) = `r apa_num(19.41)`, *p* < `r apa_p(.001)`, $\hat{\eta}^{2}_{G}$ = `r apa_num(.051)`, 90% CI `r apa_confint(.000,.260)`, with greater alpha Event-Related Synchronization (ERS) after the administration of stereotype threat ($M_{\text{post-threat}}$ = `r apa_num(10.00)`, 95% CI `r apa_confint(-4.38,24.39)`).
A main effect of threat was also found in the upper alpha range, *F*(1, 21) = `r apa_num(15.42)`, *p* < `r apa_p(.001)`, $\hat{\eta}^{2}_{G}$ = `r apa_num(.053)`, 90% CI `r apa_confint(.000, .263)`, with greater upper alpha ERS after the administration of stereotype threat ($M_{\text{post-threat}}$ = `r apa_num(3.75)`, 95% CI `r apa_confint(-10.09, 17.59)`).
Comparing the upper alpha power directly before and after stereotype threat with one another, reached significance, *F*(1, 21) = `r apa_num(15.28)`, *p* < `r apa_p(.001)`, $\hat{\eta}^{2}_{G}$ = `r apa_num(.085)`, 90% CI `r apa_confint(.000, .308)`, with an increase after the manipulation. 
For the lower alpha power, the same comparison was significant, *F*(1, 21) = `r apa_num(4.46)`, *p* = `r apa_p(.047)`, $\hat{\eta}^{2}_{G}$ = `r apa_num(.032)`, 90% CI `r apa_confint(.000, .227)`, with an increase after the manipulation.
H1 is partially supported by this paper, while stereotype threat did result in increased neural activity, the paper did not explicitly investigate stereotype effects on any of the mentioned areas. However, parts that are associated with the DMN were affected. Furthermore, performance was not found to be inhibited to a significant degree under stereotype threat.

@krendlNegativeConsequencesThreat2008 used functional magnetic resonance imaging (fMRI) to investigate underlying neural processes of stereotype threat, specifically women under maths stereotype threat.
Twenty-eight ($N = 28$) female undergraduates were randomly assigned to either a stereotype threat or a control condition.
Neural activation patterns and maths performance (measured by accuracy, i.e., number of correct maths items; reaction time on maths problems) were used as dependent variables, stereotype threat condition (threat vs. control) and time of measurements (Time 1: pre-manipulation vs. Time 2: post-manipulation) functioned as independent variables.  
For performance, a significant condition $\times$ time interaction was found, *F*(1,26) = `r apa_num(11.41)`, *p* < `r apa_p(.005)`, $\eta^{2}_{p}$ = `r apa_p(.31)`.
Individuals under stereotype threat performed slightly worse over time, *t*(13) = `r apa_num(1.98)`, *p* = `r apa_p(.07)`).
No main effect of condition was found on performance.
The threatened group showed heightened activity in the ventral anterior cingulate cortex (vACC; BA 32/10) during the second test.
Significant interactions for BA47, *F*(1,26) = `r apa_num(7.35)`, *p* < `r apa_p(.02)`, and a trend for BA40, *F*(1,26) = `r apa_num(2.93)`, *p* < `r apa_p(.1)`, were found.
Threatened participants did show increased vACC activation over time, *t*(13) = `r apa_num(5.64)`, *p* < `r apa_p(.001)`, compared to controls, resulting in a significant interaction, *F*(1,26) = `r apa_num(5.97)`, *p* = `r apa_p(.02)`.
A significant three-way interaction was found for BA47, *F*(1,26) = `r apa_num(13.94)`, *p* < `r apa_p(.005)`, left BA 40, *F*(1,26) = `r apa_num(10.99)`, *p* < `r apa_p(.005)`, left BA 39 *F*(1,26) = `r apa_num(11.31)`, *p* < `r apa_p(.005)`, and right BA39, *F*(1,26) = `r apa_num(13.39)`, *p* < `r apa_p(.005)`.
Heightened activation, for threatened individuals, was found in the affective region (vACC).
Regarding H1, neural activation across different brain areas and networks, was found in this study, furthermore, heightened activation of vACC, which is part of the DMN, further support it. 
However, BA47 is part of the prefrontal cortex and BA40, as well as BA39 are part of the DMN, all three areas only showed increased activation in the control group, not the threatened group; thus more evidence against H1 is found in this paper. 
These findings do point out a significant flaw in H1, more on that in the discussion section.

@mangelsEmotionBlocksPath2012 investigated the effects of stereotype threat on maths performance and neutral responses to feedback using three event-related potentials (ERPs): anterior P3 (P3a), medial frontal feedback-related negativity (FRN) and posteriorly-maximal late positive potential (LPP).
The study design was prospective, with sixty-eight participants ($N = 68$) in total.
Stereotype threat vs. no stereotype threat formed the independent variable, maths performance (first-test vs. retest accuracy), ERP responses to feedback, use of the tutor (number of uses and clicks when in use), and learning success (error correction on retest) were used as dependent variables. 
While maths performance was impaired under stereotype threat, *F*(1,64) = `r apa_num(4.3)`, *p* < `r apa_p(0.05)`, it did not affect retest performance or error correction.
While LPP and learning success were closely linked, particularly under threat.
Participants showing greater initial detection of negative feedback (indicated by FRN differences) were more likely to disengage from tutor exploration. 
Those struggling to regulate attention and arousal in response to negative feedback (indicated by LPP differences) benefited less from the tutor. 
Relating these results to H1, only neural activation is supported by this paper, as the results of the affected areas are more vague, partially due to the ERPs not being significantly influenced by stereotype threat, and partially because it is not possible to link LPP, FRN, and P3a to the suggested brain areas/networks, if so, only to a small degree.  

@wuDegreeCentralityBrain2021 examined the effects of maths stereotype threat using resting-state fMRI and degree centrality (DC) analysis on 48 female Chinese undergraduates. 
Significant main effects were found for the hippocampus, middle cingulate gyrus (MCG), right cerebellum, and left precentral gyrus (PCG), using a 2 (test: pre- vs post-test) $\times$ 2 (condition: stereotype threat vs. control) mixed-effect analysis for the binary graph.
However, out of these only MCG had increased RSDC *z*-values under stereotype threat, *F*(1,45) = `r apa_num(4.883)`, *p* = `r apa_p(0.032)`.
Further, an interaction was found to be significant between test and condition in the left cerebellum anterior lobe, left hippocampus, left precuneus, and left middle occipital gyrus (MOC).
Here, the mean RSDC *z*-values were only higher in the stereotype threat condition in the right superior parietal gyrus, left precuneus, left MOG, and right angular gyrus.
The weighted graph analysis showed similar patterns, with increased RSDC z-values under threat in the middle cingulate gyrus and the aforementioned regions, except for the left cerebellum, which showed lower values.
For interactions, lower RSDC *z*-values under stereotype threat were only found for the left cerebellum (F(1, 45) = `r apa_num(4.228)`, *p* = `r apa_p(0.046)`).
H1 is partially supported by this paper, increases in the DMN (associated areas) were found as well as neural activation. However, it is unclear whether performance did suffer as a result of stereotype threat and further, while the ACC and prefrontal cortex are mentioned in the researcher's hypothesis, they are not mentioned in the results.

An overview of the included papers for Hypothesis 1 can be found in Table \ref{tab:h1_table}.
```{r h1_table, results = "asis"}
h1_table <- data.frame(
  Citation = character(),
  Study_Design = character(),
  Population = character(),
  Questions = character(),
  Variables = character(),
  data_analysis = character(),
  results = character(),
  review = character(),
  stringsAsFactors = FALSE
)

h1_table[1, ] <- c(
  "Beilock et al. (2007)",
  "Experimental",
  "Female college students in US",
  "Behavioral tasks",
  "Stereotype threat, working memory efficiency",
  "ANOVA",
  "Reduced performance on high-demand problems under threat",
  "Yes"
)

h1_table[2, ] <- c(
  "Dunst et al. (2013)",
  "Experimental",
  "58 secondary school students in Austria",
  "EEG",
  "Stereotype threat, neural efficiency, task performance",
  "ANOVA",
  "Higher cortical activation under threat",
  "Partially"
)

h1_table[3, ] <- c(
  "Forbes et al. (2015)",
  "Experimental",
  "58 participants (25 White, 33 minorities)",
  "EEG",
  "DMN phase-locking, error estimates, self-doubt",
  "Regression models",
  "DMN phase-locking may mitigate stereotype threat effects",
  "Yes"
)

h1_table[4, ] <- c(
  "Forbes et al. (2008)",
  "Experimental",
  "57 minority undergraduates",
  "EEG",
  "ERN, Pe, task performance",
  "Repeated measures analysis",
  "Smaller ERN amplitudes under threat",
  "Partially"
)

h1_table[5, ] <- c(
  "Jończyk et al. (2022)",
  "Experimental",
  "23 female undergraduates in US",
  "EEG",
  "Creativity, alpha power",
  "Repeated measures ANOVA",
  "Increased alpha power after threat",
  "Partially"
)

h1_table[6, ] <- c(
  "Krendl et al. (2008)",
  "Experimental",
  "28 female undergraduates",
  "fMRI",
  "Neural activation, maths performance",
  "Mixed-model ANOVA",
  "Increased vACC activation, decreased cognitive region activation under threat",
  "Partially"
)

h1_table[7, ] <- c(
  "Mangels et al. (2012)",
  "Prospective",
  "68 participants",
  "EEG",
  "Maths performance, ERP responses, learning success",
  "ANOVA",
  "LPP and learning success link more pronounced under threat",
  "Partially"
)

h1_table[8, ] <- c(
  "Wu and Zhao (2021)",
  "Experimental",
  "48 female undergraduates in China",
  "RS-fMRI",
  "RSDC of brain regions",
  "Mixed-effect analysis",
  "Increased RSDC in DMN areas, decreased in cerebellum and hippocampus",
  "Partially"
)

apa_table(
  h1_table,
  caption = "Overview of the Included Papers for Hypothesis 1",
  longtable = TRUE,
  escape = FALSE,
  landscape = TRUE,
  col.names = c(
    "Citation",
    "Study Design",
    "Population",
    "Research Questions",
    "Variables",
    "Methods of Data Analysis",
    "Results",
    "Hypothesis confirmed"
  ),
  align = c("m{1.5cm}", "m{3cm}", "m{2.5cm}", "m{3cm}", "m{3cm}", "m{3cm}", "m{3.5cm}", "m{1.5cm}"),
  note = "This table summarizes studies investigating neural activation patterns under stereotype threat. The 'Variables' column focuses on brain areas and networks of interest, such as the amygdala, prefrontal cortex, default mode network, and salience network. 'Methods of Data Analysis' includes neuroimaging techniques like fMRI and EEG. 'Results' highlight changes in neural activation patterns related to stereotype threat."
)
```


## Hypothesis 2: Stereotype threat, cognitive control.

@guardabassiWeightStatusWeight2020 hypothesized that BMI and working memory were negatively, whether this effect was increased by stereotype threat, and whether this effect can be moderated by endorsement.
Body Mass Index (BMI), stereotype threat condition (threat vs. control), personal endorsement of obesity-related stereotypes (stereotype endorsement), and weight-based teasing, as independent variables, working memory performance (*N*-back task performance; 0-back up to two-back) was used as the dependent variable.
The final sample consisted of 176 primary school children, 106 of which were boys ($M_{\text{age}}$ = 116.07 months, *SD* = `r apa_num(10.43)`).
A significant main effect was found for *N*-back difficulty, F(2, 198.70) = `r apa_num(43.43)`, *p* < `r apa_p(.001)`, and the condition $\times$ *z*BMI interaction, F(1, 153.07) = `r apa_num(5.07)`, *p* = `r apa_p(.026)`.
Under stereotype threat, *z*BMI scores negatively correlated with working memory.
H2 is weakly supported by this paper, while stereotype threat did decrease *N*-back task performance, it cannot be divided which parts of working memory were affected, since the *N*-back task does involve multiple parts of working memory.

@hirnsteinGenderstereotypingCognitiveSex2014 investigated the effects of stereotype threat on sex differences in cognitive performance and its relation to testosterone levels. 
A final sample of 136 participants ($n_{\text{female}} = 70$) were tested in a 2 (stereotype threat vs. control) $\times$ 2 (mixed vs. same sex) $\times$ 2 (male vs. female) factorial design, which formed the independent variables.
Cognitive performance (tested using mental rotation, verbal fluency, and perceptual speed tests) alongside testosterone levels, were used as dependent variables.
The MRT-3D showed a significant main effect of Sex, with men performing better than women, *F*(1,128) = `r apa_num(10.97)`, *p* = `r apa_p(.001)`, $\eta^{2}$ = `r apa_num(.08)`, *d* = `r apa_num(0.57)`, while Condition showed a significant main effect in the MP-2D, *F*(1,128) = `r apa_num(4.70)`, *p* = `r apa_p(.032)`, $\eta^{2}$ = `r apa_num(.04)`.
For verbal fluency, interactions were found between Condition and Group Sex Composition, in both, the WF, *F*(1,128) = `r apa_num(4.49)`, *p* = `r apa_p(.036)`, $\eta^{2}$ = `r apa_num(.03)`,and the 4W, *F*(1,128) = `r apa_num(6.30)`, *p* = `r apa_p(.013)`, $\eta^{2}$ = `r apa_num(.05)`).
Between Sex $\times$ Condition, another interaction was found, in the 4W, *F*(1,128) = `r apa_num(6.77)`, *p* = `r apa_p(.011)`, $\eta^{2}$ = `r apa_num(.05)`.
Furthermore, in the 4W, Condition showed a significant main effect, *F*(1,128) = `r apa_num(4.67)`, *p* = `r apa_p(.033)`, $\eta^{2}$ = `r apa_num(.04)`.
PS also showed the significant Condition and Group Sex Composition interaction, *F*(1,128) = `r apa_num(6.89)`, *p* = `r apa_p(.009)`, $\eta^{2}$ = `r apa_num(.05)`.
Condition, again showed a significant main effect, this time in the PS, *F*(1,128) = `r apa_num(12.65)`, *p* = `r apa_p(.001)`, $\eta^{2}$ = `r apa_num(.09)`.
H2 is weakly but partially being supported, since individuals under stereotype threat performed worse on the 4W (but not WF) and perceptual speed tests, which measure cognitive control among other things.

In this study, the @jordanoPrimingPerformancerelatedConcerns2017 investigated the effects of stereotype threat on both, cognitive performance and task-related mind-wandering.
In both experiments sixty female undergraduates were assigned to either a stereotype threat or control condition; mind-wandering — measured using Task-Unrelated Thoughts (TUTs) and Task-Related Inference (TRI) probes —, task performance (on the Operation Span task; OSPAN), and self-reported measures (i.e., emotional states, cognitive load/perceived difficulty, experience of mind-wandering), were used as dependent variables.
In the first experiment, it was found that participants under stereotype threat reported significantly more TRI compared to the control group, *F*(1,58) = `r apa_num(5.669)`, *p* = `r apa_p(0.021)`, *d* = `r apa_num(0.636)`.  
Neither maths verification accuracy nor letter recall accuracy were worse under stereotype threat.
In the second experiment, the same pattern was found, with participants under stereotype threat reporting significantly more TRI, *F*(1,58) = `r apa_num(5.527)`, *p* = `r apa_p(0.022)`, *d* = `r apa_num(0.423)`.
Maths verification accuracy was worse under stereotype threat, *F*(1,58) = `r apa_num(12.11)`, *p* = `r apa_p(0.001)`, *d* = `r apa_num(0.164)`.
H2 is partially confirmed. While cognitive control did suffer under stereotype threat, as evidenced by increased mind-wandering (TRI), regardless of task difficulty, task performance only worsened in the more difficult maths component of the OSPAN task.

@krendlNegativeConsequencesThreat2008 has already been reported in the H1 section.
H2 is supported, due to decreased accuracy under stereotype threat, as well as neural activation patterns (vACC, DLPFC, IFG, BA47, BA40).

@linEffectStereotypeThreat2023 investigated the mediating role of executive function in stereotype threat effects on spatial perspective-taking tasks.
Stereotype threat (threat vs. control) served as the independent variable, while spatial perspective-taking performance and executive function performance (inhibition, updating, shifting) were used as dependent variables.
Seventy-six undergraduates participated 
A significant decrease in performance was found for the threat group, *F*(1,74) = `r apa_num(10.06)`, *p* = `r apa_p(.002)`, $\eta^{2}$ = `r apa_num(.12)`).  
In Experiment 2, seventy-seven undergraduates participated.  
The effect of stereotype threat was significant for inhibition and updating, *F*(1,75) = `r apa_num(11.40)`, *p* = `r apa_p(.001)`, $\eta^{2}$ = `r apa_num(.13)`), and *F*(1,75) = `r apa_num(5.54)`, *p* = `r apa_p(.021)`, $\eta^{2}$ = `r apa_num(.07)`), respectively.
Females under threat performed worse on the spatial perspective-taking task.
Only inhibition showed a significant (indirect) mediating effect.
Further, between spatial perspective-taking and stereotype threat, a significant direct effect was found, $\text{direct effect}$ = `r apa_num(.38)`, *SE* = `r apa_num(.18)`, *t* = `r apa_num(2.06)` 95% $\text{CI}$ `r apa_confint(0.0128,0.7460)`, also, significant negative effects of stereotype threat on inhibition (*b* = -`r apa_num(.73)`, *SE* = `r apa_num(0.22)`, *t* = -`r apa_num(3.38)` CI `r apa_confint(-1.5114, -0.2979)`) and updating (*b* = -`r apa_num(.52)`, *SE* = `r apa_num(0.22)`, *t* = -`r apa_num(2.35)`, 95% CI `r apa_confint(-0.9608, -0.0800)`) were found.
H2 is partially supported by this paper, as cognitive control (updating and inhibition) and performance did suffer under stereotype threat; however, shifting did not reach significance.  

@rydellStereotypeThreatExecutive2014 examined the effects of stereotype threat on executive functions and maths performance across three experiments.
The independent variable was condition (stereotype threat vs. control), while maths performance, executive function (inhibition, updating, shifting), and risk-taking behaviour functioned as dependent variables.
In the first experiment, 168 ($n_{\text{female}}$ = 75) undergraduates participated.
Stereotype threat significantly impaired women's inhibition, *F*(1,164) = `r apa_num(7.95)`, *p* = `r apa_p(.005)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.046)`) and updating, *F*(1,164) = `r apa_num(20.89)`, *p* < `r apa_p(.001)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.113)`.
A performance decrease under threat was found, for accuracy, *F*(1,164) = `r apa_num(20.22)`, *p* < `r apa_p(.001)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.110)`.  
Experiment 2 used a sample of ninety female undergraduates.
Regarding maths performance, under threat, accuracy, *t*(88) = -`r apa_num(3.15)`, *p* = `r apa_p(.002)`, *d* = -`r apa_num(.66)` and the correct item count, *t*(88) = -`r apa_num(5.15)`, *p* < `r apa_p(.001)`, *d* = -`r apa_num(1.09)` were impaired, with updating mediating this effect.  
In Experiment 3, a sample of eighty-two female undergraduates participated.
Inhibition, *t*(79) = -`r apa_num(2.34)`, *p* = `r apa_p(.02)`, *d* = -`r apa_num(.50)`, and updating, *t*(79) = -`r apa_num(2.29)`, *p* = `r apa_p(.03)`, *d* = -`r apa_num(.50)`, were significantly affected by stereotype threat
The results for maths performance, showed accuracy, *t*(79) = -`r apa_num(3.28)`, *p* = `r apa_p(.01)`, *d* = -`r apa_num(.704)`, and the correct item count, *t*(79) = -`r apa_num(2.14)`, *p* = `r apa_p(.035)`, *d* = -`r apa_num(.48)` being impaired.
Under threat, women were more likely to take risks; however, no correlation between it and maths performance was found.
The paper more so supports H2 than it does not. Shifting repeatedly did not reach significance, while the other executive functions did.  

@stahlRolePreventionFocus2012 investigated the role of regulatory focus in stereotype threat effects on cognitive control and maths performance across three experiments. 
The study used varying combinations of independent variables: condition (stereotype threat vs. no threat), regulatory focus (prevention focus vs. promotion focus vs. no focus), and task order (maths task first vs. maths task last). 
Dependent variables were cognitive control capacity (measured by a Stroop task) and maths performance (accuracy and response time on an MA task).
Sixty-three social science students ($n_{\text{female}}$ = 50) participated in Experiment 1, one hundred eight social science students ($n_{\text{female}}$ = 82, $n_{\text{male}}$ = 26) in Experiment 2, and one hundred sixty-four female students in Experiment 3.
A significant effect of stereotype threat on Stroop inference was found, *F*(1,61) = `r apa_num(8.69)`, *p* = `r apa_p(.004)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.13)`. 
Experiment 2 found a main effect of threat, *F*(1,102) = `r apa_num(8.91)`, *p* = `r apa_p(.004)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.08)`.
Further, Experiment 1's results for the Stroop task, were replicated, *F*(1, 101) = `r apa_num(2.80)`, *p* < `r apa_num(.10)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.03)`, and an interaction on Stroop inferences were found, *F*(2,101) = `r apa_num(3.07)`, *p* = `r apa_p(.05)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.06)`).
The Stroop inference was only significant under threat, in the prevention condition, *F*(1,101) = `r apa_num(3.6)`, *p* = `r apa_p(.24)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.01)`.  
In Experiment 3, an interaction was found to be significant on maths performance (% of correct responses), *F*(1,150) = `r apa_num(13.30)`, *p* < `r apa_p(.001)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.08)`.
Furthermore, only in the prevention focus condition, when the maths task came first, individuals under threat were found to perform better.
For maths performance, measured as RT, the same three-way interaction was significant, *F*(1,152) = `r apa_num(4.69)`, *p* = `r apa_p(.03)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.03)`.
For the maths first condition, prevention focus results in better performance under threat.
In the maths last condition, the two-way interaction was marginally significant.
H2 is mostly supported by this paper, albeit, only under prevention focus - and here also only after the initial temporary increase in cognitive control (Experiment 3).

@wisterMentioningMenstruationStereotype2013 hypothesized that menstruation stereotype threat would impair performance on cognitive tasks, this effect would be amplified if women believed menstruation to be a hindrance to their cognitive abilities.
However, if menstruation was primed as a positive influence, cognitive performance would not be impaired.
Ninety-two female undergraduates were assigned into four groups, 2 stereotype threat (menstruation threat vs. no threat) $\times$ 2 menstruation prime (positive vs. no positive prime), forming the independent variables, while cognitive performance (measured by a Stroop test and SAT-like maths test) and menstrual attitudes (measured by Menstrual Attitude Questionnaire; MAQ) were used as dependent variables.
The experiment ended for everyone with the completion of the Menstrual Attitudes Questionnaire.  
While a main effect of threat on Stroop performance was found, Lambda = `r apa_num(.874)`, *F*(1,68) = `r apa_num(4.909)`, *p* < `r apa_p(.01)`.
Participants under threat were able to complete less items correctly, *F*(1,69) = `r apa_num(9.48)`, *p* < `r apa_num(.01)`, and a correlation between closeness to menstruation and both, Stroop performance, *r* = -`r apa_num(0.557)`, *p* = `r apa_p(.011)`, and positive prime effectiveness, *r* = -`r apa_num(0.460)`, *p* = `r apa_p(.61)` were found, with individuals in the Menstruation Threat/Positive Prime condition performing worst. 
H2 is partially supported by this paper, cognitive performance under threat did only suffer if measured on the Stroop task, further, the prime also influenced performance.  

@wulandariTrustYourAbilities2020 hypothesized that how gender-stereotype threat is being activated, affects performance differently, depending on gender and task difficulty.
Participants were assigned to one of four groups, differing in the gender-stereotype threat activation (blatant vs. moderately explicit vs. subtle vs. control), forming the independent variables, alongside gender (male vs. female) and task difficulty (easy vs. medium vs. hard), while letter fluency performance (number of correct words/errors) and cognitive processes (clusterings/switching) were used as dependent variables.
The sample consisted of 168 undergraduates ($n_{\text{female}}$ = 91).  
No significant effect was found for switching, neither for gender, nor for threat; for cluster size, only a significant effect of gender was found, *F*(1,159) = `r apa_num(4.123)`, *p* < `r apa_p(0.05)`, $\eta^{2}_{\text{p}}$ = `r apa_p(0.025)`, with males scoring higher than females.
Also, positive correlations between total errors and gender-stereotype score, *r* = `r apa_num(0.222)`, *p* < `r apa_p(0.01)`, were found, with gender-stereotype score being the result of the gender-stereotype questionnaire. 
H2 is not supported by this paper, more so, it provides evidence against it.  

An overview of the included papers for Hypothesis 2 can be found in Table \ref{tab:h2_table}.
```{r h2_table, results = "asis"}
h2_table <- data.frame(
  Citation = character(),
  Study_Design = character(),
  Population = character(),
  Questions = character(),
  Variables = character(),
  data_analysis = character(),
  results = character(),
  review = character(),
  stringsAsFactors = FALSE
)

h2_table[1, ] <- c(
  "Guardabassi and Tomasetto (2020)",
  "Cross-sectional",
  "176 primary school children",
  "N-back task",
  "BMI, stereotype threat, working memory",
  "Mixed-effects models",
  "zBMI negatively correlated with working memory under threat",
  "Partially"
)

h2_table[2, ] <- c(
  "Hirnstein et al. (2014)",
  "Factorial",
  "136 participants (66 male, 70 female)",
  "Cognitive tests",
  "Stereotype threat, sex, group composition, cognitive performance",
  "ANOVA",
  "Performance decreased on 4W and perceptual speed under threat",
  "Weakly"
)

h2_table[3, ] <- c(
  "Jordano and Touron (2017)",
  "Experimental",
  "120 female undergraduates",
  "OSPAN task, mind-wandering probes",
  "Stereotype threat, mind-wandering, task performance",
  "ANOVA",
  "Increased mind-wandering, decreased maths performance under threat",
  "Partially"
)

h2_table[4, ] <- c(
  "Krendl et al. (2008)",
  "Experimental",
  "28 female undergraduates",
  "fMRI",
  "Neural activation, maths performance",
  "Mixed-model ANOVA",
  "Increased vACC activation, decreased cognitive region activation under threat",
  "Yes"
)

h2_table[5, ] <- c(
  "Lin et al. (2023)",
  "Cross-sectional",
  "153 female undergraduates",
  "Spatial perspective-taking, executive function tests",
  "Stereotype threat, executive function, spatial performance",
  "ANCOVA, mediation analysis",
  "Decreased performance, impaired inhibition and updating under threat",
  "Partially"
)

h2_table[6, ] <- c(
  "Rydell et al. (2014)",
  "Experimental",
  "340 undergraduates across 3 experiments",
  "Executive function tasks, maths tests",
  "Stereotype threat, executive function, maths performance",
  "ANOVA, mediation analysis",
  "Impaired inhibition and updating, decreased maths performance under threat",
  "Mostly"
)

h2_table[7, ] <- c(
  "Ståhl et al. (2012)",
  "Experimental",
  "335 students across 3 experiments",
  "Stroop task, maths task",
  "Stereotype threat, regulatory focus, cognitive control",
  "ANOVA",
  "Initial increase then decrease in cognitive control under threat (prevention focus)",
  "Mostly"
)

h2_table[8, ] <- c(
  "Wister et al. (2013)",
  "Experimental",
  "92 female undergraduates",
  "Stroop test, SAT-like maths test",
  "Menstruation threat, cognitive performance",
  "MANOVA",
  "Impaired Stroop performance under menstruation threat",
  "Partially"
)

h2_table[9, ] <- c(
  "Wulandari and Hendrawan (2020)",
  "Experimental",
  "168 undergraduates (91 female)",
  "Letter fluency test",
  "Stereotype threat activation, gender, task difficulty",
  "ANOVA",
  "No significant effects of threat on performance",
  "No"
)

apa_table(
  h2_table,
  caption = "Overview of the Included Papers for Hypothesis 2",
  longtable = TRUE,
  escape = FALSE,
  landscape = TRUE,
  col.names = c(
    "Citation",
    "Study Design",
    "Population",
    "Research Questions",
    "Variables",
    "Methods of Data Analysis",
    "Results",
    "Hypothesis confirmed"
  ),
  align = c("m{1.5cm}", "m{3cm}", "m{2.5cm}", "m{3cm}", "m{3cm}", "m{3cm}", "m{3.5cm}", "m{1.5cm}"),
  note = "This table presents studies examining cognitive control processes under stereotype threat. The 'Variables' column includes both cognitive processes (e.g., inhibition, updating, shifting) and related performance measures. 'Methods of Data Analysis' specifies cognitive tasks used, such as the Stroop task, n-back task, or task-switching paradigms. 'Results' emphasize changes in cognitive control performance under stereotype threat conditions."
)
```

## Hypothesis 3: Stereotype threat, working memory.

@bedynskaStereotypeThreatLinked2020 investigated the relationships between chronic stereotype threat, language achievement, and domain identification in a sample of 319 male secondary school students.
The study utilized chronic stereotype threat as the independent variable, while language achievement and domain identification served as dependent variables. Additionally, working memory and intellectual helplessness were examined as mediators, and gender identification was explored as a moderator.
The researchers found an overall moderate level of stereotype threat in the sample, with only a slight correlation between stereotype threat and both intellectual helplessness and working memory (*r* = `r apa_num(.32)`).
Stereotype threat did negatively impact working memory capacity, with the latter mediating the relationship between stereotype threat and language achievement, *b* = `r apa_num(2.81)`, $\beta$ = `r apa_num(0.45)`, *SE* = `r apa_num(0.06)`, *p* < `r apa_p(.001)`, 95% CI `r apa_confint(0.338,0.553)`.
Language achievement was indirectly affected by stereotype threat, through impaired working memory and intellectual helplessness.
H3 is supported by this paper; however it should be noted that it was chronic stereotype threat that was investigated and that the level of threat was only moderate.  

@bedynskaChronicStereotypeThreat2018 examined the effects of chronic stereotype threat on mathematical achievement in a sample of 624 female secondary school students. 
The study employed chronic stereotype threat as the independent variable and mathematical achievement as the dependent variable, with working memory and intellectual helplessness serving as mediators and gender identification as a moderator. 
The researchers found a slight correlation between stereotype threat and intellectual helplessness (*r* = `r apa_num(0.2)`),while maths achievement showed significant correlations with working memory (*p* < `r apa_p(0.01)`), and both stereotype threat and intellectual helplessness (*p* < `r apa_p(0.01)`), with the former being positive and the latter negative.
Working memory was negatively impacted by chronic stereotype threat, *b* = -`r apa_num(0.012)`, $\beta$ = -`r apa_num(0.113)`, *SE* = `r apa_num(0.128)`, *p* = `r apa_p(0.378)`, albeit not significantly.
Gender identity did moderate the effect of stereotype threat on working memory, amplifying the negative effect, *b* = -`r apa_num(0.006)`, $\beta$ = -`r apa_num(0.288)`, *SE* = `r apa_num(0.140)`, *p* = `r apa_p(0.039)`.
H3 is supported by this paper; however, it needs to be noted that it was chronic stereotype threat that was investigated.  

@beilockStereotypeThreatWorking2007 was already discussed in the H1 section.
H3 is supported by this paper, clear impairments on maths performance are found. 

@brownThreatDoesNot2016 investigated the effects of stereotype threat on mind-wandering in 73 female undergraduates, using the Sustained Attention to Response Task (SART). 
The study employed a 2 $\times$ 2 design with condition (stereotype threat vs. control) and SART framing (related to maths ability vs. unrelated to maths ability) as independent variables, and mind-wandering (measured by SART performance) as the dependent variable. The researchers hypothesized that participants under threat would show more mind-wandering, unless the SART was framed as related to maths ability, in which case they would show less mind-wandering due to increased motivation and effort. 
Both manipulations were successful. 
In the Stereotype Threat/SART Related condition, commission errors were fewer (*M* = `r apa_num(4.89)`, *SD* = `r apa_num(3.03)`), compared to Stereotype Threat/SART Unrelated (*M* = `r apa_num(10.44)`, *SD* = `r apa_num(4.55)`), *F*(1, 69) = `r apa_num(28.78)`, *p* < `r apa_p(.001)`, $\eta^{2}_{\text{p}}$ `r apa_num(.294)`, anticipations were lower in the Stereotype Threat/SART Related condition (*M* = `r apa_num(0.56)`, *SD* = `r apa_num(1.10)`), compared to Stereotype Threat/SART Unrelated (*M* = `r apa_num(4.44)`, *SD* = `r apa_num(7.09)`), *F*(1, 69) = `r apa_num(11.42)`, *p* < `r apa_p(.01)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.142)`, and RT coefficient of variation showed less variability in the Stereotype Threat/SART Related condition (*M* = `r apa_num(258)`, *SD* = `r apa_num(76)`), compared to Stereotype Threat/SART Unrelated (*M* = `r apa_num(341)`, *SD* = `r apa_num(97)`), *F*(1, 69) = `r apa_num(11.75)`, *p* < `r apa_p(.001)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.146)`.
H3 is not supported by this paper, as the mere effort account was found to be the more likely explanation for the results.  

@guardabassiWeightStatusWeight2020 was already discussed in the H2 section.
H3 is supported by this paper, as *N*-back task performance was found to be impaired under stereotype threat.  

@hutchisonGoalsCanBe2013 examined the effects of stereotype threat on mind-wandering and Stroop task performance in a sample of 187 men (88.5% Caucasian). The study used working memory capacity (measured by OSPAN), list congruency (mostly congruent vs. mostly incongruent), and stereotype threat condition (threat vs. control) as independent variables, while Stroop task performance (error rates and reaction times) served as the dependent variable. The researchers hypothesized that mind-wandering would increase under threat, impairing Stroop task performance, particularly in incongruent trials.
While the two-way interaction between stereotype threat and working memory capacity was moderate, $\beta$ = -`r apa_num(0.11)`, *t* = -`r apa_num(1.93)`, *p* = `r apa_p(.054)`, a main effect was found for stereotype threat, $\beta$ = `r apa_p(.12)`, *t* = `r apa_num(2.11)`, *p* < `r apa_p(.05)`, showing the Stroop effect to be larger under threat.
Further, the interaction with list congruency was found to qualify this main effect, with mostly congruent lists, $\beta$ = `r apa_p(.24)`, *t* = `r apa_num(2.55)`, *p* < `r apa_p(.05)`, showing a greater Stroop effect under threat, than mostly incongruent lists, $\beta$ = -`r apa_num(.02)`, *t* = -`r apa_num(0.17)`, *p* = `r apa_p(.86)`, 
Building on this, the interaction between all independent variables was found to be significant, $\beta$ = -`r apa_num(.12)`, *t* = -`r apa_num(1.99)`, *p* < `r apa_p(.05)`.
Reaction times on the Stroop task were also decreased under threat to a significant degree, $R^2$ = `r apa_p(.53)`, *F*(7, 174) = `r apa_num(28.95)`, *p* < `r apa_p(.001)`.  
H3 is partially supported, a significant effect of threat on Stroop performance was only found for low working memory capacity individuals. 
Further, working memory capacity might moderate the effect.  

@jamiesonMereEffortStereotype2007 investigated the effects of stereotype threat on tasks requiring inhibitory control across four experiments. 
The study used condition (stereotype threat vs. control), task type (anti-saccade vs. pro-saccade), and cognitive load (2-back vs. 0-back task) as independent variables, while accuracy, reaction time (RT), and eye movements served as dependent variables.
Experiment 1 displayed the target in the saccade task for 150 ms, Experiment 2, 3, and 4 for 250 ms.
In Experiment 1 the sample consisted of eighty undergraduates, Experiments 2 and 3 had thirty-six female undergraduates, and Experiment 4 seventy-two.
Performance on the anti-saccade task was impaired for participants under threat, compared to controls, *F*(1, 72) = `r apa_num(17.28)`, *p* < `r apa_p(.001)`, *d* = `r apa_num(0.98)`.
The interaction between Condition $\times$ Task indicated that under threat, response times were lower, to a significant degree, *F*(1, 72) = `r apa_num(4.85)`, *p* = `r apa_p(.05)`, further, under threat, accuracy was also higher for the anti-saccade trails, *F*(1, 32) = `r apa_num(9.06)`, *p* = `r apa_p(.01)`, *d* = `r apa_num(1.06)`, while it was lower for pro-saccade trails, *F*(1, 32) = `r apa_num(8.30)`, *p* = `r apa_p(.01)`, *d* = `r apa_num(1.01)`.  
In Experiment 2, RTs were, again, faster under threat in both saccade tasks, *F*(1, 32) = `r apa_num(19.52)`, *p* < `r apa_p(.001)`, *d* = `r apa_num(1.58)`).
In Experiment 3, RT was lower in the stereotype threat condition, *F*(1, 32) = `r apa_num(30.74)`, *p* < `r apa_p(.001)`, *d* = `r apa_num(1.96)`.
Further, contrasts showed that this was true for both the anti- and pro-saccade tasks, *F*(1, 32) = `r apa_num(29.53)`, *p* < `r apa_p(.001)`, *d* = `r apa_num(1.91)` and *F*(1, 32) = `r apa_num(43.47)`, *p* < `r apa_p(.001)`, *d* = `r apa_num(2.34)`, respectively - the same can be said for the adjusted reaction times from the eye movements, *F*(1, 31) = `r apa_num(10.06)`, *p* = `r apa_p(.01)`, *d* = `r apa_num(1.12)`.  
In Experiment 4, *n*-back task performance did not differ between controls and participants under threat, neither did accuracy.
Previous results for reaction time under threat were only replicated for the 0-back condition, *F*(1, 64) = `r apa_num(13.67)`, *p* = `r apa_p(.01)`, *d* = `r apa_num(0.93)`, while the 2-back condition showed a reduction in speed for participants under threat, *F*(1, 64) = `r apa_num(12.15)`, *p* = `r apa_p(.01)`, *d* = `r apa_num(0.87)`.
H3 is mostly not supported by this paper, only the slower reaction times under high cognitive load indicate decrease working memory speed (it is not a direct measure of working memory speed), while the other results rather support the mere effort account, which is an alternative hypothesis to the working memory account.  

@johnsStereotypeThreatExecutive2008 conducted a series of experiments to examine the effects of stereotype threat on working memory capacity, attention allocation to anxiety-related stimuli, and maths performance. 
The study used condition (stereotype threat vs. control), emotion regulation strategy, anxiety measure description, and ethnicity as independent variables, while working memory capacity, attention allocation, maths performance, and self-reported anxiety served as dependent variables.
In Experiment 1, eighty-one Caucasian female students participated
In the working memory task, women were able to recall fewer words under threat, resulting in a main effect of threat, *F*(1, 77) = `r apa_num(9.53)`, *p* < `r apa_p(.01)`.
A significant Condition $\times$ Anxiety measure description interaction was found for attention allocation, *F*(1, 77) = `r apa_num(6.41)`, *p* = `r apa_p(.01)`, with more attention given to anxiety-related stimuli under threat when the task was framed as a measure of perceptual focus. 
Experiment 3 had sixty-one Caucasian women participating.
Working memory performance did suffer under stereotype threat; however, just in the threat only condition, *t*(55) = `r apa_num(2.31)`, *p* < `r apa_p(.05)`, *d* = `r apa_num(0.62)`, the same results were found for maths test performance, *t*(55) = `r apa_num(2.11)`, *p* < `r apa_p(.05)`, *d* = `r apa_num(0.64)`.
Working memory performance was found to mediate the relationship between stereotype threat and maths performance, $\beta$ = `r apa_p(.30)`, *p* < `r apa_p(.05)`.
In Experiment 4, thirty-four Latino (22 women) and forty-seven Caucasians (28 women) participated.
In the threat only condition, anxiety-related words received less attention by Latinos, *t*(71) = `r apa_num(2.47)`, *p* < `r apa_p(.05)`, *d* = `r apa_num(0.7)`.
Working memory performance was significantly impaired for Latinos under only stereotype threat, *t*(71) = `r apa_num(2.18)`, *p* < `r apa_p(.05)`, *d* = `r apa_num(0.55)`.
Further, Caucasians in the threat only condition recalled the most words, while Latinos and Caucasians did not significantly differ in performance in the anxiety reappraisal condition.
H3 is supported by this paper.  

@penningtonStereotypeThreatMay2019 conducted two experiments to investigate the effects of positive and negative stereotypes on cognitive performance. 
The study used stereotype condition as the independent variable, with levels varying between experiments. 
Experiment 1 used self-as-target stereotype threat, group-as-target stereotype threat, and no-threat control, while Experiment 2 employed negative/positive group-as-target stereotype threat and non-threat control. 
The dependent variables included anti-saccade task performance measures and, in Experiment 2, maths task performance.
In Experiment 1, participants were sixty-four female undergraduates.
One of the manipulation checks was significant, while the other was not.
For the anti-saccade task, neither SRT for correct saccades, nor their accuracy revealed a significant main effect of stereotype threat, *F*(2, 58) = `r apa_num(0.30)`, *p* = `r apa_p(0.75)`, $\eta^{2}_{\text{p}}$ = `r apa_p(0.01)`), and *F*(2, 57) = `r apa_num(0.03)`, *p* = `r apa_p(0.97)`, $\eta^{2}_{\text{p}}$ < `r apa_p(0.001)`, respectively.
The same can be said for reflexive saccades and their SRTs, *F*(2, 57) = `r apa_num(0.03)`, *p* = `r apa_p(0.97)`, $\eta^{2}_{\text{p}}$ < `r apa_p(0.001)`, and *F*(2, 56) = `r apa_num(0.25)`, *p* = `r apa_p(0.78)`, $\eta^{2}_{\text{p}}$ = `r apa_p(0.009)`, respectively.
While the SRTs for corrective saccades, again, did not reach significance for stereotype threat, *F*(2, 53) = `r apa_num(0.3)`, *p* = `r apa_p(.75)`, $\eta^{2}_{\text{p}}$ = `r apa_p(0.01)`, the percentage of corrective saccades did, *F*(2, 57) = `r apa_num(3.57)`, *p* = `r apa_p(.0035)`, $\eta^{2}_{\text{p}}$ = `r apa_p(0.11)`.  
The sample in Experiment 2 consisted of sixty female undergraduates.
The manipulation checks were successful.
On the anti-saccade task, no significant main effects were found for any of the performance measures, the same can be said for the MA task.
This paper does not support H3. In Experiment 1 there is weak evidence of a few impairments; however, overall stereotype threat did not seem to significantly alter performance.  

@rydellMultipleSocialIdentities2009 hypothesized that different social identities can mitigate the performance impairments of stereotype threat.
Further, a positive social identity can lighten the depletion of working memory capacity under stereotype threat.  
Gender stereotype (present vs. absent) and college student stereotype (present vs. absent) were the independent variables, while working memory capacity alongside maths performance and vowel counting accuracy were the dependent variables.
Fifty-seven ($N = 57$) female undergraduates participated in the study.
A significant two-way interaction was found between both stereotype conditions, *F*(1, 53) = `r apa_num(6.01)`, *p* = `r apa_p(.02)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.102)`, without gender-stereotypes, performance did not differ between the college student stereotype conditions.
Further, under gender-stereotype threat, maths performance did suffer to a significant degree.
Working memory showed the same pattern, with, the two-way interaction being significant, *F*(1, 53) = `r apa_num(4.91)`, *p* = `r apa_p(.03)`, $\eta^{2}_{\text{p}}$ = `r apa_p(0.08)`, the without gender stereotypes conditions showing no significant differences, *F*(1, 27) = `r apa_num(2.33)`, *p* = `r apa_p(.14)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.008)`. 
The number of words recalled was lower, for those under gender-stereotype threat, who did not have the college student stereotype, *F*(1, 26) = `r apa_num(31.41)`, *p* < `r apa_p(.001)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.547)`.
Working memory capacity mediated the relationship of both stereotypes and maths performance, as analysed with a Sobel test, *z* = `r apa_num(1.96)`, *p* = `r apa_p(.05)`.
H3 is supported by this paper.  

@schmaderMetacognitivePerspectiveCognitive2009 conducted two experiments to examine the relationship between anxiety, stereotype threat, and working memory capacity. 
The study used prime condition (confidence vs. doubt) and self-reported anxiety as independent variables in both experiments, with additional variables of ethnicity in Experiment 1 and task frame in Experiment 2. 
Working memory performance, measured by a modified Reading Span Test, served as the dependent variable.
The final sample in Experiment 1 consisted of 37 minorities (17 Hispanics, 16 African Americans, and 4 American Indian) and 40 Whites ($N = 77$).
While the Prime $\times$ Ethnicity interaction did not reveal a main effect on anxiety, a marginal one was found for ethnicity, *F*(1, 73) = `r apa_num(2.92)`, *p* = `r apa_p(.09)`.
For working memory, the sentence reading times did not differ significantly between conditions.  
In Experiment 2, the final sample consisted of 111 females (79 White, 10 Hispanic, 7 African American, 7 Asian American, 1 American Indian, and 7 unidentified; $N = 111$).  
A prime $\times$ task frame interaction was found for anxiety, *F*(1, 107) = `r apa_num(3.83)`, *p* = `r apa_p(.05)`, with anxiety being higher in the maths test condition, compared to the problem-solving task; however, significance was not reached, while also not reaching significance, the opposite pattern was found for women in the confidence condition.
For working memory the three-way interaction among task frame, prime, and anxiety level was significant, $\beta$ = -`r apa_num(.2)`, *p* = `r apa_p(.05)`.
If the task was framed to be diagnostic (stereotype threat), the anxiety $\times$ prime interaction was significant, $\beta$ = -`r apa_num(.3)`, *p* < `r apa_p(.04)`, with higher anxiety and doubt resulting in significantly lower working memory performance, while lower anxiety showed no effects, independently of the prime.
H3 is partially supported by this paper, as Study 1 does not support it, while Study 2 does.  

@schmaderConvergingEvidenceThat2003 conducted three experiments to investigate the effects of stereotype threat on working memory capacity and maths test performance. 
The study used condition (stereotype threat vs. control) as an independent variable across all experiments, with additional variables of gender in Experiment 1 and ethnicity in Experiment 2. 
maths test performance and working memory capacity served as dependent variables.
In Experiment 1, the final sample consisted of 51 (28 female) undergraduates.
Working memory capacity under threat was also significantly lower than in the control condition, *F*(1, 54) = `r apa_num(23.84)`, *p* < `r apa_p(.001)`.
Women under threat recalled fewer words than any other condition, *F*(1, 54) = `r apa_num(15.69)`, *p* < `r apa_p(.001)`.
Further, women under threat spent longer on each equation, showing a marginal main effect of stereotype threat, *F*(1, 54) = `r apa_num(3.44)`, *p* < `r apa_p(.1)`; however, no significant differences were found for accuracy (equations solved correctly) between the conditions.  
Experiment 2 had a final sample of 72 ($N = 72$) undergraduates, 33 of which were Latino (20 women), and 39 White (27 women).
Latinos under threat were the lowest performing group, reaching significantly lower scores than Whites under threat, *F*(1, 58) = `r apa_num(6.45)`, *p* < `r apa_p(.05)`, *d* = `r apa_num(0.66)` and Latinos in the control condition, *F*(1, 58) = `r apa_num(4.19)`, *p* < `r apa_p(.05)`, *d* = `r apa_num(0.55)`.
A Gender $\times$ Stereotype Threat interaction was also found, *F*(1, 58) = `r apa_num(5.21)`, *p* < `r apa_p(.05)`.
In Experiment 3, the final sample consisted of 28 female undergraduates ($N = 28$).
Under stereotype threat, while absolute span scores were lower, *t*(26) = `r apa_num(3.13)`, *p* < `r apa_p(.01)`, *d* = `r apa_num(1.19)`.
Under threat, accuracy was impaired, *t*(26) = `r apa_num(2.38)`, *p* < `r apa_p(.05)`, while effort (number of attempted problems) was not.
Regression analysis revealed that working memory capacity significantly predicted maths performance , $\beta$ = `r apa_p(.58)`, *t*(26) = `r apa_num(3.26)`, *p* < `r apa_p(.01)`, while the direct effect of threat became non-significant when controlling for working memory, $\beta$ = -`r apa_num(.12)`, *t*(26) = -`r apa_num(0.66)`, *p* = `r apa_p(.5)`.
A Sobel test confirmed the mediating role of working memory (*z* = `r apa_num(2.26)`, *p* < `r apa_p(.02)`). 
H3 is supported by this paper.  

@tineGenderRaceIncomebased2013 examined how different types of stereotype threat (gender-, race-, and income-based) affect maths performance and working memory, and whether these threats can have cumulative effects. 
The study used gender (male vs. female), race (White vs. racial/ethnic minority), income level (low, middle, high), and number of stigmatized aspects of identity (0 to 3) as independent variables, while post-test scores of both maths performance and working memory performance served as dependent variables. 
Seventy-one undergraduates ($N=71$) participated, 46 female, 24 racial/ethnic minority (17 Black/African American, 7 Hispanic/Latino), and 15 low-income, all of these were considered to have a stigmatized aspect of identity, with some having multiple.  
For gender-based stereotype threat, working memory performance was affected significantly, *F*(1, 68) = `r apa_num(4.91)`, *p* < `r apa_p(.05)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.067)`, but not maths performance
Under race-based stereotype threat, both maths and working memory performance were impaired, *F*(1, 68) = `r apa_num(16.73)`, *p* < `r apa_p(.001)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.197)` and *F*(1, 68) = `r apa_num(7.41)`, *p* < `r apa_p(.001)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.098)`, respectively.
Both, maths, *F*(2, 67)^[corrected to plausible values for F, since it was reported as *F*(12 67)] = `r apa_num(5.92)`, *p* < `r apa_p(.01)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.150)` and working memory performance, *F*(2, 67) = `r apa_num(4.92)`, *p* < `r apa_p(.05)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.128)`, were also lower under income-based threat.
The number of stigmatized aspects significantly predicted both maths and working memory performance, with participants having three stigmatized aspects performing significantly worse than those with zero, particularly in working memory, *F*(3, 66) = `r apa_num(6.82)`, *p* < `r apa_p(.001)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.227)`.
The amount of effort did not differ under gender- or race-based threat; however, low-income participants reported to have put in more effort into the task, so did the two stigmatized aspects group; each compared to their counterparts.
H3 is supported by this paper.  

@vanlooExperienceFeelingPowerful2013 investigated how power priming might shield women from the negative effects of stereotype threat on maths performance, hypothesizing that this protection would occur through maintained working memory capacity. 
The study employed power prime (high, low, control) and stereotype threat condition (stereotype threat vs. no threat) as independent variables, while working memory capacity, maths performance, and threat-based concern served as dependent variables. 
The Positive and Negative Affect Schedule (PANAS) was used as a control variable.  
The final sample consisted of 131 ($N = 131$) female undergraduates.  
Both, stereotype threat, *F*(1, 125) = `r apa_num(39.46)`, *p* < `r apa_p(.001)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.240)`, and power prime, had a significant main effect on working memory capacity, the two-way interaction qualified these results, *F*(2, 125) = `r apa_num(13.38)`, *p* < `r apa_p(.001)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.18)`).
Under threat, working memory was lower for women with low power or in the control condition, *F*(1, 125) = `r apa_num(50.05)`, *p* < `r apa_p(.001)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.27)`, *F*(1, 125) = `r apa_num(15.5)`, *p* < `r apa_p(.001)`, $\eta^{2}_{\text{p}}$ = `r apa_p(.11)`, respectively.
Maths performance showed similar results across the board.
Working memory capacity mediated the relationship between power and stereotype threat, $\beta$ = -`r apa_num(.36)`, *p* < `r apa_num(.001)`, further a positive and significant correlation between maths performance and working memory was found, $\beta$ = `r apa_p(.62)`, *p* < `r apa_num(.001)`.
Using a Sobel test, it was found that, in the relationship between maths performance and the power $\times$ stereotype threat interaction, working memory capacity was a significant mediator, *z* = -`r apa_num(3.53)`, *p* < `r apa_p(.001)`.
H3 is mostly supported by this hypothesis, only when primed with high power, stereotype threat did not impair working memory capacity.  

An overview of the included papers for Hypothesis 2 can be found in Table \ref{tab:h3_table}.

```{r h3_table, results = "asis"}
# Create the data frame with the necessary columns
h3_table <- data.frame(
  Citation = character(),
  Study_Design = character(),
  Population = character(),
  Questions = character(),
  Variables = character(),
  data_analysis = character(),
  results = character(),
  review = character(),
  stringsAsFactors = FALSE
)

h3_table[1, ] <- c(
  "Bedyńska et al. (2020)",
  "Cross-sectional",
  "319 male secondary school students",
  "Working memory tasks",
  "Chronic stereotype threat, working memory, language achievement",
  "Mediation analysis",
  "Stereotype threat negatively impacted working memory capacity",
  "Yes"
)

h3_table[2, ] <- c(
  "Bedyńska et al. (2018)",
  "Cross-sectional",
  "624 female secondary school students",
  "Working memory tasks",
  "Chronic stereotype threat, working memory, maths achievement",
  "Mediation analysis",
  "Working memory mediated stereotype threat and maths achievement",
  "Yes"
)

h3_table[3, ] <- c(
  "Beilock et al. (2007)",
  "Experimental",
  "Female college students in US",
  "Modular Arithmetic task",
  "Stereotype threat, working memory efficiency",
  "ANOVA",
  "Reduced performance on high-demand problems under threat",
  "Yes"
)

h3_table[4, ] <- c(
  "Brown and Harkins (2016)",
  "Experimental",
  "73 female undergraduates",
  "SART, maths test",
  "Stereotype threat, SART framing, mind-wandering",
  "ANOVA",
  "Support for mere effort account, not working memory impairment",
  "No"
)

h3_table[5, ] <- c(
  "Guardabassi and Tomasetto (2020)",
  "Cross-sectional",
  "176 primary school children",
  "N-back task",
  "BMI, stereotype threat, working memory",
  "Mixed-effects models",
  "zBMI negatively correlated with working memory under threat",
  "Yes"
)


h3_table[6, ] <- c(
  "Hutchison et al. (2013)",
  "Experimental",
  "187 men",
  "Stroop task, OSPAN",
  "Working memory capacity, stereotype threat, Stroop performance",
  "Regression analysis",
  "Stroop effect larger under threat for low WMC individuals",
  "Partially"
)

h3_table[7, ] <- c(
  "Jamieson and Harkins (2007)",
  "Experimental",
  "224 undergraduates across 4 experiments",
  "Saccade tasks, N-back task",
  "Stereotype threat, task type, cognitive load",
  "ANOVA",
  "Support for mere effort account in most conditions",
  "Mostly No"
)

h3_table[8, ] <- c(
  "Johns et al. (2008)",
  "Experimental",
  "176 participants across 3 experiments",
  "Working memory task, maths test",
  "Stereotype threat, emotion regulation, working memory",
  "ANOVA, mediation analysis",
  "Working memory impaired under threat, mediated maths performance",
  "Yes"
)

h3_table[9, ] <- c(
  "Pennington et al. (2019)",
  "Experimental",
  "124 female university students",
  "Anti-saccade task, maths task",
  "Stereotype condition, task performance",
  "ANOVA",
  "No significant effects of threat on performance",
  "No"
)

h3_table[10, ] <- c(
  "Rydell et al. (2009)",
  "Experimental",
  "57 female undergraduates",
  "Vowel counting task, maths problems",
  "Gender stereotype, college student stereotype, working memory",
  "ANOVA, mediation analysis",
  "Working memory capacity mediated stereotype effects on maths performance",
  "Yes"
)

h3_table[11, ] <- c(
  "Schmader et al. (2009)",
  "Experimental",
  "188 participants across 2 experiments",
  "Reading Span Test",
  "Stereotype threat, anxiety, working memory",
  "Regression analysis",
  "Anxiety predicted lower working memory under stereotype threat",
  "Partially"
)

h3_table[12, ] <- c(
  "Schmader and Johns (2003)",
  "Experimental",
  "159 undergraduates across 3 experiments",
  "OSPAN, maths test",
  "Stereotype threat, working memory capacity, maths performance",
  "ANCOVA, mediation analysis",
  "Working memory capacity reduced under threat, mediated maths performance",
  "Yes"
)

h3_table[13, ] <- c(
  "Tine and Gotlieb (2013)",
  "Experimental",
  "71 undergraduates",
  "Maths test, working memory test",
  "Multiple stereotype threats, maths and working memory performance",
  "ANOVA",
  "Working memory impaired under various stereotype threats",
  "Yes"
)

h3_table[14, ] <- c(
  "Van Loo and Rydell (2013)",
  "Experimental",
  "131 female undergraduates",
  "Letter-memory task, maths test",
  "Power prime, stereotype threat, working memory",
  "ANOVA, mediation analysis",
  "High power prime protected working memory from stereotype threat effects",
  "Mostly"
)

# Create the apa_table object
apa_table(
  h3_table,
  caption = "Overview of the Included Papers for Hypothesis 3",
  longtable = TRUE,
  escape = FALSE,
  landscape = TRUE,
  col.names = c(
    "Citation",
    "Study Design",
    "Population",
    "Research Questions",
    "Variables",
    "Methods of Data Analysis",
    "Results",
    "Hypothesis confirmed"
  ),
  align = c("m{1.5cm}", "m{3cm}", "m{2.5cm}", "m{3cm}", "m{3cm}", "m{3cm}", "m{3.5cm}", "m{1.5cm}"),
  note = "This table outlines studies investigating working memory impairment under stereotype threat. The 'Variables' column focuses on working memory measures and associated performance indicators. 'Methods of Data Analysis' details specific working memory tasks employed, such as complex span tasks, operational span tasks, or reading span tests. 'Results' highlight changes in working memory capacity and performance under stereotype threat."
)
```

# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
